### 2023-06-08 paper/localpsf.tex
add summary to computational cost section

>>>>

In summary, computing all the necessary ingredients to evaluate kernel entries of the PSF approximation requires a handful of operator applies (e.g., $6+\nbatch$ operator applies in two dimensions, or $10+\nbatch$ operator applies in three dimensions, with $\nbatch$ typically in the range 1--25), plus comparatively cheap additional overhead costs, most notably performing ellipsoid intersection tests while choosing sample point batches. Once these ingredients are computed, no more operator applies are required, and approximate kernel entries can be evaluated fast. Constructing the H-matrix from kernel entries requires a number of elementary operations that scales nearly linear in $N$. Using the resulting H-matrix to perform further linear algebra operations also scales nearly linearly in $N$, though the details of these costs depend heavily on the type of H-matrix and operation being performed.
